DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-05 paper/overview.tex

Despite aforementioned issues, the trained models were still able to
achieve a reasonable degree of accuracy, successfully navigating
several different tracks we trained. The source code, build
instruction, and a collection of self-driving videos of the DeepPicar
can be found at: \url{https://github.com/heechul/picar}.
%% \begin{center}
%% \end{center}

>>>>

Despite the aforementioned issues, the trained models were still able to
achieve a reasonable degree of accuracy, successfully navigating
several different tracks we trained. The source code, build
instruction, and a collection of self-driving videos of the DeepPicar
can be found at: \url{https://github.com/heechul/picar}.
%% \begin{center}
%% \end{center}
